30June16 explant sups plate 3: MIG, RANTES, IL1ra

### 2016-07-12 30June16_plate_3_explant_sup.Rmd
Added plot titles, fixed inline code

---
title: '30June16 explant sups plate 3: MIG, RANTES, IL1ra'
author: "Claire Levy"
date: "July 6, 2016"
output: github_document

---
This is an analysis of data from running our MSD plate 3 on some of HSV2 infected explant sup samples for Herpes P01. See explant_and_HVE_cell_sup_MSD_README for more on the different plates/analyte panels. This plate has the following analytes measured in each well

@@

The MSD machine gives the data in an excel or text format. I have .csv file with the results.

@@

@@

standardsOutOfRange<-standards%>%
  filter(Detection.Range != "In Detection Range")%>%
  arrange(Type, Assay, Sample)%>%
  select(Type,Sample, Assay, Detection.Range, X..Recovery)

@@

Of the `r length(standards)` standards that we measured, `r length(standardsInRange)` are in the detection range. The following standards were out of the detection range:
`r pander(standardsOutOfRange)`

@@

ggplot(stdFit, aes(x = Sample, y = X..Recovery))+
  geom_point(aes(color = Sample))+
  facet_wrap(~Assay)+
  theme(axis.text.x = element_text(angle=25))+
  scale_y_continuous(limits = c(75, 200))+
  geom_abline(slope = 0, intercept = c(80, 120))+
  labs(y = "Percent Recovery")

@@

MIG data

@@

MIGAvgConcExplantDat<- AvgConcExplantDat %>%
  filter(Assay == "MIG")

ggplot(data = MIGAvgConcExplantDat, aes(x = Virus, y = avgConc))+

  geom_point(aes(color = Donor, shape = Detection.Range ),size = 2 )+

  geom_line(aes(color = Donor, group = Donor))+

@@

@@

  theme(axis.text.x = element_text(angle = 25))
```

RANTES data

@@

RANTESAvgConcExplantDat<- AvgConcExplantDat %>%
  filter(Assay == "RANTES")

ggplot(data = RANTESAvgConcExplantDat, aes(x = Virus, y = avgConc))+

  geom_point(aes(color = Donor, shape = Detection.Range ),size = 2 )+

  geom_line(aes(color = Donor, group = Donor))+

@@

  theme(axis.text.x = element_text(angle = 25))
```

IL1-RA data

@@

IL1raAvgConcExplantDat<- AvgConcExplantDat %>%
  filter(Assay == "IL1-RA")

ggplot(data = IL1raAvgConcExplantDat, aes(x = Virus, y = avgConc))+

  geom_point(aes(color = Donor, shape = Detection.Range ),size = 2 )+

  geom_line(aes(color = Donor, group = Donor))+

@@

  theme(axis.text.x = element_text(angle = 25))

>>>>

---
title: '30June16 explant sups plate 3: MIG, RANTES, IL1ra'
author: "Claire Levy"
date: "July 6, 2016"
output: github_document
---
This is an analysis of data from running our MSD plate 3 on some of HSV2 infected explant sup samples for Herpes P01. See explant_and_HVE_cell_sup_MSD_README for more on the different plates/analyte panels. This plate has the following analytes measured in each well

@@

@@

#The MSD machine gives the data in an excel or text format. I have .csv file with the results.

@@

standardsOutOfRange<-standards%>%
  filter(Detection.Range != "In Detection Range")%>%
  arrange(Type, Assay, Sample)%>%
  select(Sample, Assay, Detection.Range)

@@

Of the `r nrow(standards)` standards that we measured, `r nrow(standardsInRange)` are in the detection range. The following standards were out of the detection range:
`r pander(standardsOutOfRange)`

@@

ggplot(stdFit, aes(x = Sample, y = X..Recovery))+
  geom_point(aes(color = Sample))+
  facet_wrap(~Assay)+
  theme(axis.text.x = element_text(angle=25))+
  scale_y_continuous(limits = c(75, 200))+
  geom_abline(slope = 0, intercept = c(80, 120))+
  labs(y = "Percent Recovery")+
  theme(axis.text.x = element_text(size = rel(0.8)))

@@

@@

MIGexplantDat<- explantDat %>%
  filter(Assay == "MIG")

ggplot(data = MIGexplantDat, aes(x = Virus, y = Calc..Concentration))+

  geom_point(aes(color = Donor, shape = Detection.Range ),size = 1, alpha = 0.5 )+

  stat_summary(aes(group = Donor, color = Donor),fun.y = mean, geom = "point", size = 2)+

  stat_summary(aes(group = Donor, color = Donor), fun.y =mean, geom = "line")+

@@

  labs( y = "Concentration")+

@@

  theme(axis.text.x = element_text(angle = 25))+
  ggtitle("MIG data")

@@

RANTESexplantDat<- explantDat %>%
  filter(Assay == "RANTES")

ggplot(data = RANTESexplantDat, aes(x = Virus, y = Calc..Concentration))+

  geom_point(aes(color = Donor, shape = Detection.Range ),size = 1, alpha = 0.5 )+

  stat_summary(aes(group = Donor, color = Donor),fun.y = mean, geom = "point", size = 2)+

  stat_summary(aes(group = Donor, color = Donor), fun.y =mean, geom = "line")+

@@

  theme(axis.text.x = element_text(angle = 25))+
  ggtitle("RANTES data")

@@

IL1RAexplantDat<- explantDat %>%
  filter(Assay == "IL1-RA")

ggplot(data = IL1RAexplantDat, aes(x = Virus, y = Calc..Concentration))+

  geom_point(aes(color = Donor, shape = Detection.Range ),size = 1, alpha = 0.5 )+

  stat_summary(aes(group = Donor, color = Donor),fun.y = mean, geom = "point", size = 2)+

  stat_summary(aes(group = Donor, color = Donor), fun.y =mean, geom = "line")+

@@

  theme(axis.text.x = element_text(angle = 25))+
  ggtitle("IL1-RA data")
